### 2016-08-06 forgerard.tex
change subline line breaks.  Add a few env python.  Working toward 2-dust model

\section{Model Fits}
\subsection{One-Color Model}
We hypothesize that Type Ia supernova spectral features are predictive of intrinsic
magnitudes.  The intrinsic magnitudes are not perfectly deterministic, but have some intrinsic dispersion.
An extrinsic physical process common to all supernovae can influence the propagation
of light along the line of sight to incluence apparent magnitudes.

\subsubsection{Setup}
Specifically, we assume a linear relationship between the equivalent widths of the Ca and Si spectral features
$EW_{Ca}$ and $EW_{Si}$, and the intrinsic $UBVRI$ magnitudes
with residual Gaussian dispersion with covariance $C_c$.  A grey magnitude offset $\Delta$ is included for each supernova
to capture grey intrinsic dispersion and distance errors introduced in the normalization of the photometry.
The  extrinsic process is also assumed to be linear.  The observables
$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$ and $EW_{Si,o}$ have Gaussian uncertainty with covariance $C$.  The model can be expressed
\begin{equation*}
\left(
\begin{matrix}
U\\B\\V\\R\\I
\end{matrix}
\right) \sim \mathcal{N}
\left(
\Delta +
\left(
\begin{matrix}
c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} \\
c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si}  \\
c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} \\
c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} \\
c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}
\end{matrix}
\right)
,C_{c}
\right)
\end{equation*}
\begin{equation*}
\left(
\begin{matrix}
U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}\end{matrix}
\right) \sim \mathcal{N}
\left(
\left(
\begin{matrix}
U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
EW_{Si}\\ EW_{Ca}
\end{matrix}
\right)
,C
\right)
\end{equation*}
The global parameters $c$, $\alpha$, and $\beta$ are the intercepts and slopes of the bilinear relationships between equivalent widths
and intrinsic magnitudes.  The extrinsic piece is split into the properties $\gamma$ of the physical process and the per-supernova 
parameters $k$ that indicate how much of that process each object undergoes.  To break the degeneracies inherent in the model we impose
\begin{equation*}
\langle \Delta \rangle=0, \langle k \rangle=0, \langle k^2 \rangle=1, \gamma_0 \ge 0.
\end{equation*}

@@

The best-fit distribution for the parameters $\gamma$ are shown in Figure~\ref{gamma:fig}.  Our measurement of
$\frac{\gamma_X}{\gamma_1-\gamma_2}$ and $\frac{\gamma_X}{\gamma_2}$  compared with the predictions of CCM dust:
our fit values for $\gamma$ are consistent with the  $R_V=3.1$ CCM model.  The uncertainties in the 5 measurements
of $\frac{\gamma_X}{\gamma_1-\gamma_2}$ are correlated: measurements of $\gamma_X/\gamma_2$ have significantly smaller
uncertainties and are consistent with $R_V=3.1$.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3in]{output7/gamma_corner.pdf} 
   \caption{Best-fit distribution for the parameters $\gamma$.  68\% measurements of $\frac{\gamma_X}{\gamma_1-\gamma_2}$ and CCM
   predictions for different values of $R_V$.}
   \label{gamma:fig}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output7/ccm.pdf}
      \includegraphics[width=2.8in]{output7/ccm2.pdf} 
   \caption{68\% measurements of $\frac{\gamma_X}{\gamma_1-\gamma_2}$ (left) and $\frac{\gamma_X}{\gamma_2}$ (right).  CCM
   predictions for these parameters are overlaid for different values of $R_V$.}
   \label{ccm:fig}
\end{figure}

@@

Add Si line velocity.
%
%\subsection{Two-Color Model}
%Motivated by the indication that the one-parameter linear model does not fully describe the color-magnitude data, we develop a new model.
%Considering that dust does predict a linear extinction in magnitudes, we preserve $k$ as a color parameter and the $\gamma k$ relation
%with magnitude.   A second color parameter $D$ is introduced to be quadratically related with magnitude.  Practically I have found
%that the data are not sufficient to constrain both the linear and quadratic terms of $D$, so only the latter is considered.
%
%\subsubsection{Setup}
%\begin{equation*}
%\left(
%\begin{matrix}
%U\\B\\V\\R\\I
%\end{matrix}
%\right) \sim \mathcal{N}
%\left(
%\Delta +
%\left(
%\begin{matrix}
%c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} +\delta_{10} D^2\\
%c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} +\delta_{11} D^2\\
%c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} +\delta_{12} D^2\\
%c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} +\delta_{13} D^2\\
%c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si} +\delta_{14} D^2
%\end{matrix}
%\right)
%,C_{c}
%\right).
%\end{equation*}
%%\begin{equation*}
%%D \sim \mathcal{N}(\bar{D},1)
%%\end{equation*}
%\begin{equation*}
%\left(
%\begin{matrix}
%U_o  \\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}
%\end{matrix}
%\right) \sim \mathcal{N}
%\left(
%\left(
%\begin{matrix}
%U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
%EW_{Si}\\ EW_{Ca}
%\end{matrix}
%\right)
%,C
%\right).
%\end{equation*}
%\begin{equation*}
%\langle \Delta \rangle=0, \langle k \rangle=0, \langle k^2 \rangle=1, \langle (D-\bar{D})^2 \rangle=1, \gamma_0 \ge 0.
%\end{equation*}

>>>>

\section{Model Fits}
\subsection{One-Color, One-Dust Model}
\label{onecolor:sec}
We hypothesize that Type Ia supernova spectral features are predictive of intrinsic
magnitudes.  The intrinsic magnitudes are not perfectly deterministic, but have some intrinsic dispersion.
An extrinsic physical process common to all supernovae can influence the propagation
of light along the line of sight to incluence apparent magnitudes.

\subsubsection{Setup}
Specifically, we assume a linear relationship between the equivalent widths of the Ca and Si spectral features
$EW_{Ca}$ and $EW_{Si}$, and the intrinsic $UBVRI$ magnitudes
with residual Gaussian dispersion with covariance $C_c$.  A grey magnitude offset $\Delta$ is included for each supernova
to capture grey intrinsic dispersion and distance errors introduced in the normalization of the photometry.
The  extrinsic process is also assumed to be linear.  The observables
$U_o, B_o, V_o, R_o, I_o$, $EW_{Ca,o}$ and $EW_{Si,o}$ have Gaussian uncertainty with covariance $C$.  The model can be expressed
\begin{equation}
\left(
\begin{matrix}
U\\B\\V\\R\\I
\end{matrix}
\right) \sim \mathcal{N}
\left(
\Delta +
\left(
\begin{matrix}
c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} \\
c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si}  \\
c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} \\
c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} \\
c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}
\end{matrix}
\right)
,C_{c}
\right)
\label{ew:eqn}
\end{equation}
\begin{equation}
\left(
\begin{matrix}
U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}\end{matrix}
\right) \sim \mathcal{N}
\left(
\left(
\begin{matrix}
U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
EW_{Si}\\ EW_{Ca}
\end{matrix}
\right)
,C
\right).
\label{dust:eqn}
\end{equation}
The global parameters $c$, $\alpha$, and $\beta$ are the intercepts and slopes of the bilinear relationships between equivalent widths
and intrinsic magnitudes.  The extrinsic piece is split into the properties $\gamma$ of the physical process and the per-supernova 
parameters $k$ that indicate how much of that process each object undergoes.  To break the degeneracies inherent in the model we impose
\begin{equation*}
\langle \Delta \rangle=0, \langle k \rangle=0, \langle k^2 \rangle=1, \gamma_0 \ge 0.
\end{equation*}

@@

The best-fit distribution for $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ are shown in Figure~\ref{rx:fig}.  Our measurement of
$R_X$ and $\frac{\gamma_X}{\gamma_2}$  compared with the predictions of CCM dust:
our fit values for $\gamma$ are consistent with the  $R_V=3.1$ CCM model.  The uncertainties in the 5 measurements
of $R_X$ are correlated: measurements of $\gamma_X/\gamma_2$ have significantly smaller
uncertainties and are consistent with $R_V=3.1$.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3in]{output7/rx_corner.pdf} 
   \caption{Best-fit distribution for the   $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$.
   \label{rx:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output7/ccm.pdf}
      \includegraphics[width=2.8in]{output7/ccm2.pdf} 
   \caption{68\% measurements of $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ (left) and $\frac{\gamma_X}{\gamma_2}$ (right).  CCM
   predictions for these parameters are overlaid for different values of $R_V$.}
   \label{ccm:fig}
\end{figure}

@@

Add Si line velocity.

\subsection{Two-Dust Model}

Motivated by the consistency of the external extinction with CCV $R_V=3.1$ dust, and the hint of the color-magnitude
diagrams in Figure~\ref{magresidual:fig}  not following single slopes, we develop a new model in which
each supernova encounters one of two sources of external extinction.

\subsubsection{Setup}
The model is identical to that of \S\ref{onecolor:sec} except with the addition of an alternative extrinsic source of extinction.
The intrinsic magnitudes of the supernova are determined by the spectral properties expressed as Eqn.~\ref{ew:eqn}.
One extrinsic source of extinction is modeled as before with Eqn.~\ref{dust:eqn};
the second source of extinction
is modeled similarly but with the introduction of new parameters $\gamma_{2X}$
\begin{equation}
\left(
\begin{matrix}
U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}\end{matrix}
\right) \sim \mathcal{N}
\left(
\left(
\begin{matrix}
U +\gamma_{20} k \\B +\gamma_{21} k \\V+\gamma_{22} k\\R+\gamma_{23} k\\I+\gamma_{24} k\\
EW_{Si}\\ EW_{Ca}
\end{matrix}
\right)
,C
\right).
\label{dust2:eqn}
\end{equation}
The probability that a supernova experiences the first source of extinction is given by the free parameter $p_0$,
the probability of the second is $1-p_0$.  
The same $k$ parameters are used to describe supernovae in both extinction sources.  In order to do this we change
some of the conditions that constrain the degeneracies of the model
\begin{equation*}
\langle \Delta \rangle=0, \gamma_1 = 1+\gamma_2, \gamma_{21}=1+\gamma_{22}.
\end{equation*}
These conditions are useful for interpreting the extinction as being due to dust, as $R_X = \gamma_X$,
the color excess $E(B-V) \equiv (\gamma_1-\gamma_2)k =k$.
The $c$ parameters  are fit such that both extinction models
revert to the same intrinsic magnitudes for $k=0$: the $\langle k \rangle=0$ condition is removed.

To alleviate the degeneracies inherent to mixture models, we set the range of $\gamma$'s for the first extinction source to be within
a range of CCM possibilities.  No such restriction is placed on the $\gamma_{2X}$'s of the second source.

\subsubsection{Results}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output9/rx_corner.pdf}
      \includegraphics[width=2.8in]{output9/rx1_corner.pdf} 
   \caption{Best-fit distribution for the first extinction source  $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ (left) and
   the second extinction source
   $R_{2X}=\frac{\gamma_{2X}}{\gamma_{21}-\gamma_{22}}$ (right).
   \label{rx:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output9/ccm.pdf}
      \includegraphics[width=2.8in]{output9/ccm2.pdf} 
         \includegraphics[width=2.8in]{output9/ccm12.pdf}
      \includegraphics[width=2.8in]{output9/ccm22.pdf} 
   \caption{68\% measurements of $R_X=\frac{\gamma_X}{\gamma_1-\gamma_2}$ (left) and $\frac{\gamma_X}{\gamma_2}$ (right).  CCM
   predictions for these parameters are overlaid for different values of $R_V$.}
   \label{ccm:fig}
\end{figure}

%
%\subsection{Two-Color Model}
%Motivated by the indication that the one-parameter linear model does not fully describe the color-magnitude data, we develop a new model.
%Considering that dust does predict a linear extinction in magnitudes, we preserve $k$ as a color parameter and the $\gamma k$ relation
%with magnitude.   A second color parameter $D$ is introduced to be quadratically related with magnitude.  Practically I have found
%that the data are not sufficient to constrain both the linear and quadratic terms of $D$, so only the latter is considered.
%
%\subsubsection{Setup}
%\begin{equation*}
%\left(
%\begin{matrix}
%U\\B\\V\\R\\I
%\end{matrix}
%\right) \sim \mathcal{N}
%\left(
%\Delta +
%\left(
%\begin{matrix}
%c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} +\delta_{10} D^2\\
%c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} +\delta_{11} D^2\\
%c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} +\delta_{12} D^2\\
%c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} +\delta_{13} D^2\\
%c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si} +\delta_{14} D^2
%\end{matrix}
%\right)
%,C_{c}
%\right).
%\end{equation*}
%%\begin{equation*}
%%D \sim \mathcal{N}(\bar{D},1)
%%\end{equation*}
%\begin{equation*}
%\left(
%\begin{matrix}
%U_o  \\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o}
%\end{matrix}
%\right) \sim \mathcal{N}
%\left(
%\left(
%\begin{matrix}
%U +\gamma_0 k \\B +\gamma_1 k \\V+\gamma_2 k\\R+\gamma_3 k\\I+\gamma_4 k\\
%EW_{Si}\\ EW_{Ca}
%\end{matrix}
%\right)
%,C
%\right).
%\end{equation*}
%\begin{equation*}
%\langle \Delta \rangle=0, \langle k \rangle=0, \langle k^2 \rangle=1, \langle (D-\bar{D})^2 \rangle=1, \gamma_0 \ge 0.
%\end{equation*}
